Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-04 Paper.tex
\linkdest{r}{r} \linkdest{s}{s}

We declare that a signature is invalid unless all the following conditions are true:
\begin{align}
0 < r &< \mathtt{\tiny secp256k1n} \\
0 < s &< \mathtt{\tiny secp256k1n} \div 2 + 1 \\
v &\in \{27,28,\mathtt{\tiny chain\_{\mathrm{id}}} \times 2 + 35, \mathtt{\tiny chain\_{\mathrm{id}}} \times 2 + 36\}
\end{align}
where:
\begin{align}
\mathtt{\tiny secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}

>>>>

We declare that a signature is invalid unless all the following conditions are true:
\begin{align}
0 < \linkdest{r}{r} &< \mathtt{\tiny secp256k1n} \\
0 < \linkdest{s}{s} &< \mathtt{\tiny secp256k1n} \div 2 + 1 \\
v &\in \{27,28,\mathtt{\tiny chain\_{\mathrm{id}}} \times 2 + 35, \mathtt{\tiny chain\_{\mathrm{id}}} \times 2 + 36\}
\end{align}
where:
\begin{align}
\mathtt{\tiny secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}
